---
title: "**Assignment Week 4: Hospital comparison**"
output: html_notebook
---
The data for this assignment come from the [Hospital Compare web site] (http://hospitalcompare.hhs.gov) run by the U.S. Department of Health and Human Services. The purpose of the web site is to provide data and information about the quality of care at over 4,000 Medicare-certified hospitals in the U.S. This dataset covers all major U.S. hospitals.

## Plot the 30-day mortality rate for heart attack 

```{r}
outcome <- read.csv("outcome-of-care-measures.csv", colClasses = "character")
head(outcome)
```
Death mortality rates (column 11) are character, convert to numeric, then plot histogram
```{r}
outcome[, 11] <- as.numeric(outcome[,11])
hist(outcome[,11])
```

## Finding the best hospital in a state 


```{r}

best <- function(state, outcome) {
        y <-read.csv("outcome-of-care-measures.csv")
        #y[ ,c(11,17,23)] <- sapply(y[ ,c(11,17,23)],suppressWarnings(as.numeric))
        
        names(y)[c(11,17,23)] <- c("heart attack", "heart failure", "pneumonia")
        
        y[ ,11] <- suppressWarnings(as.numeric(y[ ,11])) 
        y[ ,17] <- suppressWarnings(as.numeric(y[ ,17]))
        y[ ,23] <- suppressWarnings(as.numeric(y[ ,23]))
        
        if (!state %in% y[,7]) {
            stop ("invalid state")  
        }
        if (!outcome %in% c("heart attack", "heart failure", "pneumonia")) {
            stop ("invalid outcome")  
        }
        y1 <- y[(y$State == state),]
        rank <- rank(y1[,outcome], ties.method = "min", na.last = TRUE)
        y2 <- y1$Hospital.Name[ which (rank == 1)] 
        y2
      
        
}

best("MD", "heart attack")


```

## Ranking hospitals by outcome in a state 

```{r}
rankhospital <- function (state, outcome, num = "best") {
        y <-read.csv ("outcome-of-care-measures.csv")
        #y[ ,c(11,17,23)] <- sapply(y[ ,c(11,17,23)],suppressWarnings(as.numeric))
        
        names(y)[c(11,17,23)] <- c("heart attack", "heart failure", "pneumonia")
        
        ## coerce character columns (outcome) to numeric, suppress warning
        y[ ,11] <- suppressWarnings(as.numeric(y[ ,11])) 
        y[ ,17] <- suppressWarnings(as.numeric(y[ ,17]))
        y[ ,23] <- suppressWarnings(as.numeric(y[ ,23]))
        
        if (!state %in% y[,7]) {
            stop ("invalid state")  ## if passed state is invalid, throw error 
        }
        if (!outcome %in% c("heart attack", "heart failure", "pneumonia")) {
            stop ("invalid outcome")  ## same as above for outcome 
        }
      
        y1 <- y[(y$State == state),]        ## keep only subset of passed state 
        y1 <- y1[!is.na(y1[outcome]),]      ## through out rows with NA for outcome
        y1 <- y1[order(y1$Hospital.Name),]  ## order hosp names alphabetically 
        y1$rank <- rank(y1[,outcome], ties.method = "first", na.last = TRUE)
        
      
        if (num == "best") num = min(y1$rank)
        if (num == "worst") num = max(y1$rank)
        if (num > max(y1$rank)) return (NA)
        
        y2 <- y1$Hospital.Name[ which (y1$rank == num)] 
        y2
}


rankhospital("MD", "heart attack", 2)
```


## Ranking hospitals in all states 
This does not 
```{r}
library(dplyr)
library(tidyr)
rankall <- function (outcome, num = "best") {
           y <- read.csv("outcome-of-care-measures.csv")
        #y[ ,c(11,17,23)] <- sapply(y[ ,c(11,17,23)],suppressWarnings(as.numeric))
        
        names(y)[c(11,17,23)] <- c("heart attack", "heart failure", "pneumonia")
        
        y[ ,11] <- suppressWarnings(as.numeric(y[ ,11])) 
        y[ ,17] <- suppressWarnings(as.numeric(y[ ,17]))
        y[ ,23] <- suppressWarnings(as.numeric(y[ ,23]))
        
        if (!outcome %in% c("heart attack", "heart failure", "pneumonia")) {
            stop ("invalid outcome")  
        }
        
      
         y1 <- y %>%
          group_by(State) %>%
          arrange(Hospital.Name, .by_group = TRUE) %>%
          mutate (rank = row_number(.data[[outcome]])) ##using .data from rland  
                                                      ## to pass string args from function  
        
        if (num == "best") num = min(y1$rank)
        if (num == "worst") num = max(y1$rank)
        #if (num > max(y1$rank)) return (NA) ## throws an error
        
        y2 <- y1 %>%
            group_by(State)%>% 
            #summarise (rank = nth(rank, 20), hospital = first(Hospital.Name))
            filter(rank == num) %>%
            ungroup() %>%
            complete(State = y1$State)
           
         
      y3 <- y2 %>% select(State, Hospital.Name)
      return (y3)
         
        'y2 <- subset(y1, rank == num , select = c("Hospital.Name", "State"))
        y2 <- y2[order(y2$State),]
        y2'
}


head (rankall("heart attack", 20),10)
tail (rankall("pneumonia", "worst"),3) ##this does not work yet 

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

